---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Nunito:ital,wght@0,200..1000;1,200..1000&display=swap');

body {
  font-family: "Nunito", sans-serif;
  font-size: 20px;
}
h2,h3 {
  text-decoration: underline;
}
```

## **Fuel prices across different stations in Auckland**

The purpose of this report is to get an understanding of how fuel prices compare across different fuel stations in Auckland.

```{r}
library(tidyverse)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTElqKsgASNluXUaano0vLYorvYaBtoDSF2gCqncpWcQAzg2BnE7kft1m-gm_eIMdFa0fGTrocxx_Ou/pub?gid=93307876&single=true&output=csv") %>% rename(date = 2,
                                                                                                                                                                                                              time = 3,
                                                                                                                                                                                                              unleaded_91 = 4,
                                                                                                                                                                                                              premium_95 = 5,
                                                                                                                                                                                                              premium_98 = 6,
                                                                                                                                                                                                              brand = 7,
                                                                                                                                                                                                              location = 8)

minimum_91 <- logged_data$unleaded_91 %>% min(na.rm = TRUE)
minimum_95 <- logged_data$premium_95 %>% min(na.rm = TRUE)
minimum_98 <- logged_data$premium_98 %>% min(na.rm = TRUE)

maximum_91 <- logged_data$unleaded_91 %>% max(na.rm = TRUE)
maximum_95 <- logged_data$premium_95 %>% max(na.rm = TRUE)
maximum_98 <- logged_data$premium_98 %>% max(na.rm = TRUE)

mean_91 <- logged_data$unleaded_91 %>% mean(na.rm = TRUE) %>% round(digits = 2)
mean_95 <- logged_data$premium_95 %>% mean(na.rm = TRUE) %>% round(digits = 2)
mean_98 <- logged_data$premium_98 %>% mean(na.rm = TRUE) %>% round(digits = 2)

price_means <- data.frame(Grade = c("Unleaded 91","Premium 95","Premium 98"),
                          Means = c(mean_91,mean_95,mean_98)
                          )

common_brand <- logged_data %>% count(brand)
sorted_brands <- common_brand[order(common_brand$n, decreasing = TRUE),]

unleaded91_chart <- logged_data %>% ggplot() + geom_bar(aes(x= unleaded_91), fill = "#054aed") + labs(title="Unleaded 91",x="Price ($)", y="Count")
premium95_chart <- logged_data %>% ggplot() + geom_bar(aes(x= premium_95), fill = "#e5ed05") + labs(title="Premium 95",x="Price ($)", y="Count")
premium98_chart <- logged_data %>% ggplot() + geom_bar(aes(x= premium_98), fill = "#ed0505") + labs(title="Premium 98",x="Price ($)", y="Count")
brand_chart <- logged_data %>% ggplot() + geom_bar(aes(x = brand), fill="#fc7303") + labs(title="Surveyed Brands",x="Brands", y="Count")


highest_mean <- price_means[order(price_means$Means, decreasing = TRUE),]
lowest_mean <- price_means[order(price_means$Means, decreasing = FALSE),]
```

The survey form currently holds **`r nrow(logged_data)`** records.

### Unleaded 91

```{r}
unleaded91_chart
```

The highest price for Unleaded 91 is around **$`r maximum_91`** dollars per litre and the lowest price is around **$`r minimum_91`** dollars per litre. The mean price is around **$`r mean_91`** dollars per litre.

### Premium 95

```{r}
premium95_chart
```

The highest price for Premium 95 is around **$`r maximum_95`** dollars per litre and the lowest price is around **$`r minimum_95`** dollars per litre. The mean price is around **$`r mean_95`** dollars per litre.

### Premium 98

```{r}
premium98_chart
```

The highest price for Premium 98 is around **$`r maximum_98`** dollars per litre and the lowest price is around **$`r minimum_98`** dollars per litre. The mean price is around **\$`r mean_98`** dollars per litre.

### Fuel Brands

```{r}
brand_chart
```

The most common fuel brand recorded in this survey is **`r sorted_brands$brand[1]`**.

### Summary

Comparing the means of each fuel grade in this survey, we find that **`r highest_mean$Grade[1]`** was the most expensive of all other grades with a mean price of **\$`r highest_mean$Means[1]`**, and **`r lowest_mean$Grade[1]`** was the cheapest of all other grades with a mean price of **\$`r lowest_mean$Means[1]`**.